%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Mechanical Engineer} % Job title
    {Council for Scientific and Industrial Research (CSIR)} % Organization
    {Pretoria, S.Africa} % Location
    {Feb. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implimentation of Industry 4.0 tools and software systems with a focus on Product Lifecycle Management through the use of Teamcenter.}
        \item {Mechanical Design and Simulation using Siemens NX and Simcenter 3D.}
        \item {Configuration of Virtual Reality Systems in NX.}
        \item {Optimization of Factory Floor through simulations in Technomatix Plant Simulation.}
        \item {Workshop experience with a laser cutter and water jet.}
        \item {Data analytics and GUI Design using Python.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Honours Research, Turbine Design (Dr. Glen Snedden)} % Organization
    {Pretoria, S.Africa} % Location
    {Jan. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched the effect of Surface Roughness on the aerodynamic performance of turbine blades}
        \item {Assisted in developing a spreadsheet which designs the turbine blade profile and layout from the required performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher} % Job title
    {Undergraduate Research, Vibration Analysis of Turbine Blades(Mr. Francesca Pietra)} % Organization
    {Pretoria, S.Africa} % Location
    {Jan. 2016 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Researched the whether modal analysis is a feasible method in determining crack size and location within turbine blades.}
        \item {Developed a Matlab program to analyse the vibration in a turbine blade when tapped with a hammer in order to predict modal frequencies.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Student} % Job title
    {Vacation Work, Council for Scientific and Industrial Research (CSIR)} % Organization
    {Pretoria, S.Africa} % Location
    {7 Weeks: 2015 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an optimization program and graphical user interface in Python for the efficiency optimization of Jet Engines}
        \item {Designed a mechanism in which children with walking disabilities can be assisted by their parents.}
        \item {Converted a Compressor Application written in Fortran to Python}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Student} % Job title
    {Vacation Work, EWC Consulting Engineers} % Organization
    {Mbombela, S.Africa} % Location
    {10 Weeks: 2014 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a Trommel Screen dimension calculator in python.}
        \item {Assisted in the structural design of a factory floor}
        \item {Assisted in the Maintenance of the Machinery in Malelane Sugar Mill}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
