%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Chairman} % Affiliation/role
    {Academic Commitee at Mopanie Men's Residence} % Organization/group
    {Pretoria, S.Africa} % Location
    {Jan. 2014 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained experience in leading a team of people with the academic activities in the residence.}
        \item {Obtained skills in planning and running events.}
        \item {Organized tutor sessions in which I assisted in tutoring}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Leader $\cdot$ Singer $\cdot$ Guitarist} % Affiliation/role
    {Music} % Organization/group
    {Pretoria, S.Africa} % Location
    {Jan. 2010 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Lead one of the music bands at Capital City Church International.}
        \item {Gained experience organizing sets of songs and leading the band in playing the songs effectively.}
        \item {Obtained experience singing, playing guitar and speaking in front of large groups of people.}
        \item {Gained management skills through the scheduling of people and arranging rehearsels.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Leader} % Affiliation/role
    {Church Youth} % Organization/group
    {Pretoria, S.Africa} % Location
    {Jan. 2010 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained experience working with high school youth.}
        \item {Assisted in the planning and leading of Events, Camps and Outreaches.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Community Service} % Organization/group
    {S.Africa} % Location
    {Jan. 2010 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Assisted in the construction, repair and painting of various rooms and classrooms at Hands at Work Orphanage.}
        \item {Repaired various buildings and facilities at the Bethlehem Township outside of Pretoria}
        \item {Took part in numerous church outreaches to poverty-stricken areas in South Africa, Swaziland and Mozambique.}
        \item {Repaired and cleaned various facilities at Second Chance Wildlife Rehabilitation Centre in Mbombela.}
        \item {Assisted in the repair of a childrens' playground in Pretoria.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
